%------------------------------------------------------------------------------
%------------------------------------------------------------------------------
%------------------------------------------------------------------------------
% Resume in Latex
% Author : Shubham Mazumder
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------------------------------------------------------------
%------------------------------------------------------------------------------
%------------------------------------------------------------------------------

\documentclass[letterpaper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{soul}
\input{glyphtounicode}
\usepackage[margin=0.5in]{geometry}

%----------FONT OPTIONS----------
% Sans-serif Fonts
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault,light]{inter}
% \usepackage[sfdefault]{noto-sans}
% \usepackage{roboto}
% \usepackage[sfdefault,medium]{InriaSans}
\usepackage[default]{sourcesanspro}

% Serif Fonts
% \usepackage{CormorantGaramond}
% \usepackage{charter}


% -------------------------------------
%----------PAGE SETUP------------------
% -------------------------------------


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
% \addtolength{\oddsidemargin}{0.5pt}
% \addtolength{\evensidemargin}{0.5pt}
% \addtolength{\textwidth}{0.9in}
% \addtolength{\topmargin}{-0.6in}
% \addtolength{\textheight}{1.6in}

% \addtolength{\oddsidemargin}{-.875in}
% \addtolength{\evensidemargin}{-.875in}
% \addtolength{\textwidth}{1.75in}
% \addtolength{\topmargin}{-.875in}
% \addtolength{\textheight}{1.75in}

% URL style
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% ----------- Definitions -----------------------
\def\spaceforrole{ }
\definecolor{lightyellow}{cmyk}{0.00, 0.05, 0.20, 0.00} % Highlights
\sethlcolor{lightyellow} % Highlights

%--------------- Custom commands -----------------------

\newcommand{\sectionspace}{
\vspace{-20pt}
}

\newcommand{\subheadingtitlevspace}{
\vspace{-3pt}
}


% Resume Item
\newcommand{\resumeItem}[1]{
  \item{
    {#1 \vspace{-4pt}}
  }
}

% Titles
\newcommand{\titleItem}[1]{
  % \textsl{\textbf{#1}}
  \textbf{#1}
}


% Highlighting
\newcommand{\highlight}[1]{
  \textsl{\textbf{#1}}
  % \hl{\textsl{\textbf{#1}}}
  % \textbf{#1}
  % \textsl{\hl{#1}}
}

% Resume Subheading
\newcommand{\resumeSubheading}[4]{
  \item
     \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}l@{}l}     
      {#1} & \titleItem{#3} | {#2} & \textit{#4}\\
    \end{tabular*}\vspace{-10pt}
}

% \newcommand{\resumeSubheading}[4]{
%   \item
%     \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
%       \textbf{#1} & #2 \\
%       \textit{#3} & \textit{#4} \\
%     \end{tabular*}\vspace{-8pt}
% }



% Resume Sub-sub heading
\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{#1} & \textit{#2} \\
    \end{tabular*}\vspace{-2pt}
}

% Resume Project Heading
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & \textit{ #2} \\
    \end{tabular*}\vspace{-9pt}
}

%Resume Subheading List
\newcommand{\resumeSubHeadingListStart}{\subheadingtitlevspace\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%Resume Item List
\newcommand{\resumeItemListStart}{
% \vspace{-1pt}
\begin{itemize}}
\newcommand{\resumeItemListEnd}{
% \vspace{-6pt}
\end{itemize}\vspace{-8pt}}

%-------------------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%-------------------------------------------------------

\begin{document}

% -------------------------------------
%----------HEADING---------------------
% -------------------------------------

\begin{flushleft}
    \textbf{\large Yashraj Nigam} \\    
    \textit{Gurugram, HR} $|$ 
    \textit{+91 87709 00297} $|$  
    \href{mailto:yashrajnigam97@gmail.com}{{\textit{yashrajnigam97@gmail.com}}} $|$
    \href{https://yashrajnigam.tech}{{\textit{yashrajnigam.tech}}} $|$
    \href{https://linkedin.com/in/yrnigam}{{\textit{linkedin:yrnigam}}} $|$
    \href{https://github.com/yrnigam}{{\textit{github:yrnigam}}}
    \vspace{-8pt}
\end{flushleft}
\vspace{-2pt}
% -------------------------------------
%---------- PROFESSIONAL SUMMARY ------
% -------------------------------------

\section{Professional Summary}
\vspace{-2pt}
\begin{itemize}[leftmargin=0.15in, label={}]
    {\item{
     {Experienced Data Engineer with over 4+ years of expertise, currently employed at KPMG. Proficient in Python and skilled at analyzing structured and unstructured data. Proven track record of utilizing Data Science technologies to solve real-world problems. Committed to delivering high-quality solutions and catalyzing data-driven success for organizations.} \\      
    }}
 \end{itemize}
 \sectionspace
\vspace{6pt}



% -------------------------------------
%----------TECHNICAL SKILLS------------
% -------------------------------------

\section{Technical Skills}
\subheadingtitlevspace
 \begin{itemize}[leftmargin=0.15in, label={}]
    {\item{
     \titleItem{Cloud Platform}{: AWS} \\
     \titleItem{Cloud Services}{: S3, EMR, Step functions, Glue, Lambda, SNS, Eventbridge, DataSync} \\
     \titleItem{Databases}{: Oracle, MS-SQL, Redshift, DynamoDB, MySQL, Redis, Kafka, Elasticsearch} \\
     \titleItem{ETL Tools}{: Talend (Open-Studio and Enterprise)} \\
     \titleItem{Languages}{: Python, SQL, PySpark} \\
     \titleItem{IDEs}{: Jupyter, VS Code, DBeaver , Google Colab, Databricks} \\
     \titleItem{Version Control}{: GIT, JIRA} \\
     \titleItem{Operating Systems}{: Linux, Windows} \\
     \titleItem{Libraries explored}{: Boto3, BS4, OpenCV, Scikit-learn, Pandas, SpaCy, NLTK}
    }}
 \end{itemize}
\sectionspace
\vspace{5pt}


    
% -------------------------------------
%----------EXPERIENCE------------------
% -------------------------------------

\section{Experience}
  \resumeSubHeadingListStart
      \resumeProjectHeading
           {\titleItem{{Consultant - Data Engineer}} $|$ \emph{KPMG India (Gurugram, HR)}}{November 2021 -- Present}
           \vspace{5pt}
      \resumeItemListStart
        \resumeItem{Designed and implemented a configurable ingestion job that migrated 300+ tables from Oracle to a Data Lake and Data Warehouse using Talend, Glue, and Amazon S3.}
        \resumeItem{Improved data accuracy and accessibility by designing and implementing a data pipeline using AWS Glue and PySpark.}
        \resumeItem{Reduced data processing time from 1 hour to 20 minutes, achieving significant performance and cost improvements in data pipelines and queries.}
        \resumeItem{Seamlessly integrated Talend with Python to enhance data ingestion efficiency for networked shared drives.}
        \resumeItem{Proficiently curated data in data lake's curated layer using AWS Glue, DynamoDB, Step functions, and Lambda functions, demonstrating strong AWS cloud expertise.}
        \resumeItem{Developed ETL job from scratch for data replication from Oracle DB to Oracle DB using Talend, implementing conditional checking and stored procedure calls.}
      \resumeItemListEnd
\vspace{5pt}

    \resumeProjectHeading
           {\titleItem{{Project Engineer - Data Science}} $|$ \emph{C-DAC (Hyderabad, TS)}}{September 2020 -- October 2021}
      \resumeItemListStart
        \resumeItem{Worked on a data analysis tool focused on both structured and unstructured data, encompassing over 20 modules.}
        \resumeItem{Improved code performance using in-process parallelism and multiprocessing.}
        \resumeItem{Enhanced language processing by implementing text transliteration, Named Entity Recognition (NER), and an offline language translation Python API using an open-source model.}
        \resumeItem{Utilized image and video analytics techniques, including face detection, cropping, and face matching for multimedia analysis.}
        \resumeItem{Dockerized Python code for automation and performance enhancements, streamlining deployment and scalability.}
      \resumeItemListEnd
\vspace{5pt}
    \resumeProjectHeading
           {\titleItem{{Computer Vision Engineer}} $|$ \emph{Tech Driven Basic (Indore, MP)}}{February 2020 -- August 2020}
      \resumeItemListStart
        \resumeItem{Trained deep learning model to automate the manual data entry work of invoices information.}
        \resumeItem{Created a system for multi-object detection in images using SSD and Faster R-CNN.}
        \resumeItem{Extracted invoice information through OCR, storing data in CSV files and databases.}
        \resumeItem{Utilized LabelImg for image annotation, Pytesseract for OCR, and Regular Expressions for data processing.}
        \resumeItem{Leveraged the power of Google Colab, along with OpenCV and TensorFlow, to accurately detect multiple objects in images.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

% -------------------------------------
%----------EDUCATION-------------------
% -------------------------------------

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {DAVV, Indore}{GPA: 8.2/10.0}
      {MBA in Business Analytics and Data Science}{2018 -- 2020} 
    \resumeSubheading
      {RGPV, Bhopal}{GPA: 7.3/10.0}
      {BE in Computer Science Engineering}{2014 -- 2018}
  \resumeSubHeadingListEnd
\vspace{-8pt}

% -------------------------------------
%----------HEADING---------------------
% -------------------------------------


\section{Awards and Certifications}
 \vspace{-1pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\titleItem{Super Employee and Rising Star} \emph{ $|$ KPMG, India}}{April 2022 and February 2023}
      \resumeProjectHeading
          {\titleItem{Exceptional Performer} \emph{ $|$ CDAC Hyderabad}}{April 2021}
      \resumeProjectHeading
          {\titleItem{Arctic Code Vault Contributor} \emph{$|$ GitHub}}{April 2020}
    \resumeSubHeadingListEnd




% -------------------------------------
%----------PROJECTS--------------------
% -------------------------------------

 \section{Projects}    
     \resumeSubHeadingListStart
        \resumeProjectHeading
           {\titleItem{Project 1}}{Nov 2023}
            \resumeItemListStart
            \resumeItem{In cursus turpis massa tincidunt dui. Cras pulvinar mattis nunc sed blandit libero volutpat sed. Suspendisse potenti nullam ac tortor. }
            \resumeItem{Ut consequat semper viverra nam libero justo laoreet sit amet. Feugiat nisl pretium fusce id velit ut tortor pretium.}
           \resumeItemListEnd
       \resumeProjectHeading
           {\titleItem{Project 2}}{Spring 2022}
            \resumeItemListStart
            \resumeItem{Ut consequat semper viverra nam libero justo laoreet sit amet. Feugiat nisl pretium fusce id velit ut tortor pretium.} 
            \resumeItem{In cursus turpis massa tincidunt dui. Cras pulvinar mattis nunc sed blandit libero volutpat sed. Suspendisse potenti nullam ac tortor. }
           \resumeItemListEnd
       \resumeProjectHeading
           {\titleItem{Project 3}}{November 2021}
            \resumeItemListStart
            \resumeItem{In cursus turpis massa tincidunt dui. Cras pulvinar mattis nunc sed blandit libero volutpat sed. Suspendisse potenti nullam ac tortor. }
           \resumeItemListEnd
     \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}